Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-22 paper/preprint/appendix.Rmd
activity x location using only single-location videos

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')

meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

@@

meta_long %>% filter(Activity!="N/A") %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Location, y=Activity, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6, height=10)
```

>>>>

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',')

# include videos with multiple locations
meta_long <- meta_wide %>% 
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')
  pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

single_locations = c("Bedroom","Car","Deck/Porch","Kitchen","Living Room","Off Property","Office","Outside on Property")

# single-location videos
meta_long_1loc <- meta_wide %>%
  filter(is.element(Location, single_locations)) %>%
  pivot_longer(cols = starts_with("Act."), 
               names_to = "activity_index",
               names_prefix = "Act.",
               values_to = "Activity",
               values_drop_na = T)

@@

# use meta_long for multi-location videos
meta_long_1loc %>% filter(Activity!="N/A") %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Location, y=Activity, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6, height=10)

# Talking Walk -> Taking Walk ?
# Taking Walk -> Walking?
```
